Evaluation of probabilistic photometric redshift estimation approaches for \textsc{LSST}

### 2019-09-19 paper/tex/conclusion.tex

We evaluate the twelve codes under science-agnostic metrics both established and emerging to stress-test the ensemble properties of \pzpdf\ catalogues derived by each method.
In appendices, we also present metrics of point estimates and a prevalent summary statistic of \pzpdf\ catalogues used in cosmological analyses to enable the reader to relate this work to studies of similar scope.
We observe that no one code dominates in all metrics, and that the standard metrics of \pzpdf s and the stacked estimator of the redshift distribution can be gamed by a vacuously wrong procedure that asserts the prior over the data.
We emphasize to the \pz\ community that \textbf{metrics used to vet \pzpdf\ methods must be scrutinized to ensure they correspond to the quantities that matter to our science}.

>>>>

We evaluate the twelve codes under science-agnostic metrics both established and emerging to stress-test the ensemble properties of \pzpdf\ catalogues derived by each method.
In appendices, we also present metrics of point estimates and a prevalent summary statistic of \pzpdf\ catalogues used in cosmological analyses to enable the reader to relate this work to studies of similar scope.
We observe that no one code dominates in all metrics, and that the standard metrics of \pzpdf s and the stacked estimator of the redshift distribution can be gamed by a very simplistic procedure that asserts the prior over the data.
We emphasize to the \pz\ community that \textbf{metrics used to vet \pzpdf\ methods must be scrutinized to ensure they correspond to the quantities that matter to our science}.

### 2019-09-19 paper/tex/data.tex

Correlations between SED and galaxy environment were included so as to preserve the colour-density relation of galaxy environment.
The distance to the spatially projected fifth-nearest neighbour was used as a proxy for local density in the \sdss\ training sample.
For each simulated galaxy, a galaxy with similar absolute $r$-band magnitude and local galaxy density was chosen from the training set, and that training galaxy's SED was assigned to the simulated galaxy.
In Section~\ref{sec:buzzlimitations}, we discuss the limited realism of this mock data.

@@

Given the SED, absolute $r$-band magnitude, and redshift, we computed apparent magnitudes in the six \lsst\ filter passbands, $ugrizy$.
We assigned magnitude errors in the six bands using the simple model of \citet{Ivezic:08}, assuming achievement of the full 10-year depth, with a modification of fiducial \lsst\ total numbers of 30-second visits for photometric error generation: we assume 60 visits in $u$-band, 80 visits in $g$-band, 180 visits in $r$-band, 180 visits in $i$-band, 160 visits in $z$-band, and 160 visits in $y$-band.
%numbers taken from Alex Abate's photErrorModel.py script in PhotoZDC1 repository, which was used with nYrObs=10.

@@

Following the findings of \citet{Bernstein:10}, \citet{Masters:2017} that only $~10^{4}$ spectra are necessary to calibrate \pz s to Stage IV requirements, we aimed to set aside a randomly selected training set of $3-5\times 10^{4}$ galaxies, $\sim 10\%$ of the full sample.
After all cuts described above, we designated the \textit{DC1 training set} of $44\,404$ galaxies for which observed photometry, true SEDs, and true redshifts would be provided to all codes codes and the blinded \textit{DC1 test set} of $399\,356$ galaxies for which photometry alone would be provided to all codes and \pzpdf s would be requested.
%The resulting catalogues contain $111\,171$ training galaxies and $1\,000\,883$ test galaxies.
The exact form of \lsst\ photometric filter transmission curves were also considered public information that could be used by any code.

>>>>

Correlations between SED and galaxy environment were included so as to preserve the colour-density relation of galaxy environment.
The distance to the spatially projected fifth-nearest neighbour was used as a proxy for local density in the \sdss\ training sample.
For each simulated galaxy, a galaxy with similar absolute $r$-band magnitude and local galaxy density was chosen from the training set, and that training galaxy's SED was assigned to the simulated galaxy.

@@

Given the SED, absolute $r$-band magnitude, and true redshift of each simulated galaxy, we computed apparent magnitudes in the six \lsst\ filter passbands, $ugrizy$.
We assigned magnitude errors in the six bands using the simple model of \citet{Ivezic:08}, assuming achievement of the full 10-year depth, with a modification of fiducial \lsst\ total numbers of 30-second visits for photometric error generation: we assume 60 visits in $u$-band, 80 visits in $g$-band, 180 visits in $r$-band, 180 visits in $i$-band, 160 visits in $z$-band, and 160 visits in $y$-band.
%numbers taken from Alex Abate's photErrorModel.py script in PhotoZDC1 repository, which was used with nYrObs=10.

@@

Following the findings of \citet{Bernstein:10}, \citet{Masters:2017} that only $~10^{4}$ spectra are necessary to calibrate \pz s to Stage IV requirements, we aimed to set aside a randomly selected training set of $3-5\times 10^{4}$ galaxies, $\sim 10\%$ of the full sample.
After all cuts described above, we designated the \textit{DC1 training set} of $44\,404$ galaxies for which observed photometry, true SEDs, and true redshifts would be provided to all codes and the blinded \textit{DC1 test set} of $399\,356$ galaxies for which photometry alone would be provided to all codes and \pzpdf s would be requested.
%The resulting catalogues contain $111\,171$ training galaxies and $1\,000\,883$ test galaxies.
The exact form of \lsst\ photometric filter transmission curves were also considered public information that could be used by any code.

### 2019-09-19 paper/tex/methods.tex

We test three publicly available and commonly used template-based codes that share the standard physically motivated approach of calculating model fluxes for a set of template SEDs on a grid of redshift values and evaluating a \chisq\ merit function using the observed and model fluxes:
\begin{equation} \label{eq_temp_chi}
\chi^{2}(z,T,A) = \sum_{i}^{N_{\mathrm{filt}}}\left(\frac{F^{i}_{\mathrm{obs}} - A \, F^{i}_{\mathrm{pred}}(T,z)}{\sigma^{i}_{\mathrm{obs}}}\right)^2
\end{equation}
\noindent where $A$ is a normalization factor, $F^i_{\mathrm{pred}}(T,z)$ is the flux predicted for a template $T$ at redshift $z$, $F^i_{\mathrm{obs}}$ is the observed flux in a given band $i$, $\sigma^i_{\mathrm{obs}}$ is the observed flux error, and $N_{\mathrm filt}$ is the total number of filters, in our case the six $ugrizy$ LSST filters.
In words, the likelihood is a sum of observed flux error $\sigma_{b}^{\mathrm{obs}}$-weighted squared differences between the observed flux $F^{\mathrm{obs}}_{b}$ and the normalized predicted flux $F^{\mathrm{mod}}_{b}(T, z)$ in $N_{\mathrm{filt}}$ photometric filters $b$, which is the \lsst\ $ugrizy$ filters in this case.
Specific implementation details of each code, e.~g.~prior form and implementation, are described below.

@@

Photometric Analysis for Redshift Estimate \citep[\lephare\footnote{\url{http://www.cfht.hawaii.edu/~arnouts/lephare.html}},][]{Arnouts:99,Ilbert:06} uses the $\chi^2$ of Equation~\ref{eq_temp_chi} to match observed colors with those predicted from a template set, which can be semi-empirical or entirely synthetic, directly according to the
The reported \pzpdf\ is an arbitrary normalization of the likelihood evaluated on the output redshift grid.
%\textsc{LePhare} has been used to produce the COSMOS2015 photo-$z$ catalogue \citep{Laigle:16}.

@@

In this paper, we used \texttt{xgboost} \citep{Chen:16} for the regression; it should however be noted that \texttt{FlexCode-RF}\footref{flexzboost_github}, based on Random Forests, generally performs better for smaller datasets.
As our basis $\phi_{i}(z)$, we choose a standard Fourier basis.
The two tuning parameters in our \pzpdf\ estimate are the number $I$ of terms in the series expansion and an exponent $\alpha$ that we use to sharpen the computed density estimates $\widetilde{f}(z \vert \x) \propto \widehat{f}(z \vert \x)^{\alpha}$.
Both $I$ and $\alpha$ were chosen in an automated way by minimizing the weighted $L_2$-loss function \citep[Eq. 5 in][]{Izbicki:17} on a validation set comprised of a randomly selected 15\% of the DC1 training set.
While \texttt{FlexCode}'s lossless native encoding stores each \pzpdf\ using the basis coefficients $\beta_{i}(\x)$, we discretized the final estimates into 200 linearly-spaced redshift bins $0 < z < 2$ to match the consistent output format of the experimental conditions.

>>>>

We test three publicly available and commonly used template-based codes that share the standard physically motivated approach of calculating model fluxes for a set of template SEDs on a grid of redshift values and evaluating a \chisq\ merit function using the observed and model fluxes:
\begin{equation} \label{eq_temp_chi}
\chi^{2}(z,T,A) = \sum_{i}^{N_{\mathrm{filt}}}\left(\frac{F^{i}_{\mathrm{obs}} - A \, F^{i}_{\mathrm{pred}}(T,z)}{\sigma^{i}_{\mathrm{obs}}}\right)^2
\end{equation}
\noindent where $A$ is a normalization factor, $F^i_{\mathrm{pred}}(T,z)$ is the flux predicted for a template $T$ at redshift $z$, $F^i_{\mathrm{obs}}$ is the observed flux in a given band $i$, $\sigma^i_{\mathrm{obs}}$ is the observed flux error, and $N_{\mathrm filt}$ is the total number of filters, in our case the six $ugrizy$ LSST filters.
The likelihood is a sum of observed flux error $\sigma_{b}^{\mathrm{obs}}$-weighted squared differences between the observed flux $F^{\mathrm{obs}}_{b}$ and the normalized predicted flux $F^{\mathrm{mod}}_{b}(T, z)$ in $N_{\mathrm{filt}}$ photometric filters $b$, which is the \lsst\ $ugrizy$ filters in this case.
Specific implementation details of each code, e.~g.~prior form and implementation, are described below.

@@

Photometric Analysis for Redshift Estimate \citep[\lephare\footnote{\url{http://www.cfht.hawaii.edu/~arnouts/lephare.html}},][]{Arnouts:99,Ilbert:06} uses the $\chi^2$ of Equation~\ref{eq_temp_chi} to match observed colors with those predicted from a template set.
The template set can be semi-empirical or entirely synthetic.
The reported \pzpdf\ is an arbitrary normalization of the likelihood evaluated on the output redshift grid.
%\textsc{LePhare} has been used to produce the COSMOS2015 photo-$z$ catalogue \citep{Laigle:16}.

@@

In this paper, we used \texttt{xgboost} \citep{Chen:16} for the regression; it should, however, be noted that \texttt{FlexCode-RF}\footref{flexzboost_github}, based on Random Forests, generally performs better on smaller datasets.
As our basis $\phi_{i}(z)$, we choose a standard Fourier basis.
The two tuning parameters in our \pzpdf\ estimate are the number $I$ of terms in the series expansion and an exponent $\alpha$ that we use to sharpen the computed density estimates $\widetilde{f}(z \vert \x) \propto \widehat{f}(z \vert \x)^{\alpha}$.
Both $I$ and $\alpha$ were chosen in an automated way by minimizing the weighted $L_2$-loss function \citep[Eq. 5 in][]{Izbicki:17} on a validation set comprised of a randomly selected 15\% of the DC1 training set.
While \texttt{FlexCode}'s lossless native encoding stores each \pzpdf\ using the basis coefficients $\beta_{i}(\x)$, we discretized the final estimates into 200 linearly-spaced redshift bins $0 < z < 2$ to match the consistent output format of the experimental conditions.
